Paper 3 - Tables

### 2023-05-26 docs/causal_roadmap.qmd
Using common lua filters for Quarto.

---
title: "Paper 3 - Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
  - Triangulation
  - Modified Treatment Policy
  - Mendelian Randomization
  - Metabolomics
  - Endocrine Disrupting Chemicals
  - Neurodevelopment
  - Neurobehavior
metadata-files:
  - ../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
bibliography: ../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - acronyms
  - authors-block
acronyms:
  fromfile: ../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
---

>>>>

---
title: "Paper 3 - Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
  - Triangulation
  - Modified Treatment Policy
  - Mendelian Randomization
  - Metabolomics
  - Endocrine Disrupting Chemicals
  - Neurodevelopment
  - Neurobehavior
metadata-files:
  - ../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
bibliography: ../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - ../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../all_phd/_extensions/authors-block/authors-block.lua
acronyms:
  fromfile: ../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
---

### 2023-05-26 output/paper/figures.qmd
Using common lua filters for Quarto.

---
title: "Figures"
output:
  bookdown::pdf_document2
---

```{r}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, message = FALSE, 
                      cache = TRUE)
```

<!-- ####################################################################### -->
<!-- Workflow -->
```{r}
```
<!-- ####################################################################### -->

>>>>

---
title: "Paper 3 - Figures"
format:
  pdf:
    pdf-engine: pdflatex
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
project:
  execute_dir: project
---

```{r}
#| include: false
here::i_am("figures.qmd")

library(tidyverse)
```

<!-- ####################################################################### -->
# CTD Results
<!-- ####################################################################### -->
```{r}
#| label: fig-ctd-res
#| fig.cap: Barplot CTD.
#| fig.height: 10
#| fig.width: 10
path <- "../../results/files/CTD_chem_diseases_1680702221550_05042023.csv"
ctd <- myphd::load_ctd(path = path, 
                       filter_evidence = TRUE)
myphd::plot_ctd(ctd)
```

### 2023-05-26 output/paper/manuscript.qmd
Using common lua filters for Quarto.

---
metadata-files:
  - ../../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    include-in-header:
      - \usepackage{rotating}
      - \usepackage{float}
      - \usepackage{typearea}
    pandoc_args:
      - !expr acronymsdown::add_filter()
bibliography: ../../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - /home/lorenzo/R/x86_64-pc-linux-gnu-library/4.1/acronymsdown/parse-acronyms.lua
  - ../../../../all_phd/scholarly-metadata.lua
  - ../../../../all_phd/author-info-blocks.lua
acronyms:
  fromfile: ../../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
abstract: |
 **Background**

>>>>

---
metadata-files:
  - ../../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
bibliography: ../../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - ../../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../../all_phd/_extensions/authors-block/authors-block.lua
acronyms:
  fromfile: ../../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
abstract: |
 **Background**

### 2023-05-26 output/paper/tables.qmd
Using common lua filters for Quarto.

```{r}
#| include: false
here::i_am("tables.qmd")
source("../../../../all_phd/edcs.R")
library(tidyverse)
```

@@

<!-- ####################################################################### -->
# Exposures
<!-- ####################################################################### -->
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.
edcs_info <- edcs_information() %>%
  dplyr::select(-c(chem_id, smiles))
gt::gt(edcs_info, groupname_col = "class") %>%
  gt::cols_label(
    full_name = "Compound", 
    short_name = "Symbol", 
    #smiles = "SMILES", 
    pubchem_cid = "PubChem CID", 
    ctd_id = "CTD ID", 
    exposome_explorer_id = "Exposome Explore ID", 
    parental_compound = "Parental compound"
  ) %>%
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()), 
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)), 
      gt::cell_text(weight = "bold")
    )
  ) %>%
  gt::tab_style(
    locations = gt::cells_row_groups(group = everything()), 
    style = list(gt::cell_text(weight = "bold"))
  )
```

>>>>

```{r}
#| include: false
here::i_am("tables.qmd")

library(tidyverse)
```

@@

<!-- ####################################################################### -->
# Exposures
<!-- ####################################################################### -->
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.
edcs_info <- myphd::edcs_information() %>%
  dplyr::select(-c(chem_id, smiles))
gt::gt(edcs_info, groupname_col = "class") %>%
  gt::cols_label(
    full_name = "Compound", 
    short_name = "Symbol", 
    #smiles = "SMILES", 
    pubchem_cid = "PubChem CID", 
    ctd_id = "CTD ID", 
    exposome_explorer_id = "Exposome Explore ID", 
    parental_compound = "Parental compound"
  ) %>%
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()), 
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)), 
      gt::cell_text(weight = "bold")
    )
  ) %>%
  gt::tab_style(
    locations = gt::cells_row_groups(group = everything()), 
    style = list(gt::cell_text(weight = "bold"))
  )
```
